---
title: "Instructions for Using the FindCarApp"
author: "Nina"

output: html_document
runtime: shiny
---

## Database

- The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models). For more details, see [mtcars](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html)


 
## Inputs 

#### 1. Use checkbox input to select transmission types: Manual, automatic or both.


```{r, echo=FALSE}
inputPanel(
  checkboxGroupInput('am', label=h4('Transmission Type:'), 
                                      c("Manual (1)"=1, "Automatic (0)"=0), selected= c(0,1))
)

```

#### 2. Use the slider input to select the minimum miles per gallon you require.
```{r, echo=FALSE}
inputPanel(
   sliderInput("mpg", h4("Min Miles per Gallon: "), min=10, max=35, value=10)
)
```
#### 3. Use the slider input to select the minimum gross horsepower you require.
```{r, echo=FALSE}
inputPanel(
    sliderInput("hp", h4("Min Gross Horsepower: "), min=50, max=250, value=50) 
)
```


## Outputs

####1. The average mpg of your selections

The App will calculate the average miles per gallon of the cars that you selected.

####2. List of cars meet your requirements

The App will display all the cars meet your requirement in the datatable with other features, such as weight, gear, number of cylinders, etc. 
```{r, echo=FALSE}
data(mtcars)


     
        
mycars<-cbind(rownames(mtcars),mtcars[,c(1,2,3,4,6,9,10)])
names(mycars)<-c("Model","MPG","Cylinders","Displacement", "Horsepower","Weight", "Transmission", "Gear")
renderDataTable({
                mycars[ which(mycars$Transmission %in% input$am
                          & mycars$MPG>input$mpg & mycars$Horsepower > input$hp),]})

```

